---
title: "Welcome to Fabio's Defense Website"
subtitle: "The place to find all the information you for Dr. Fabio's big day! ✨🚤👨🏻‍🎓✨"
author: "dr::Fabio Votta"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---
<h3>First thing first, kindly RSVP by clicking the button below.</h3>

```{=html}
<style>
.button {
  background-color: #144F7C; /* Blue background */
  border: none;
  color: white;
  padding: 10px 20px; /* Size of the padding around the text */
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px; /* Size of the font */
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 5px; /* Rounded corners */
  transition-duration: 0.4s; /* Smooth transition effect for hover state */
}

/* Darker background on mouse-over */
.button:hover {
  background-color: #17616A;
}
</style>
```
<br>

<center><a href="https://forms.gle/f4YLD5jomEYPTgKy7" class="button">RSVP</a></center>

<br>

<h4>Join us and celebrate as our dear Fabio becomes ...</h4>

```{r}
fabio <- paste0("Dr. ", "Fabio Votta")
print(fabio)
```

Below, you will find information about the defense and related events.

<h2>Overview</h2>

-   [Event Information](file:///C:/Users/fabio/Dropbox/postdoc/fabio_defense/fabio_defense_website.html#new-styles)

-   [New 2223](file:///C:/Users/fabio/Dropbox/postdoc/fabio_defense/fabio_defense_website.html#new-styles)

-   Event info (time, location, duration, dress code, similar to emails from other defense)

-   RSVPs link to google form where we collect emails (optional) and allow down of calendar invite - HERE add both dissertation, borrel, and party

-   Calendar invite with both dissertation + borrel and party invites - kinda like phd club

-   Link to maps dissertation + borrel and party location

-   (Optional) Summary of dissertation, maybe abstract with the hopefully cute and badass cover

-   Secret gift page with donation payment options - use IBAN, tikkie, my paypal or ask if sophia can set it up

-   Insta page + Hashtag

-   

## Dissertation Presentation Information
+ **📍Location:** Aula UvA, Singel 411, 1012 WN Amsterdam

<iframe src="https://www.google.com/maps/embed?pb=!1m14!1m8!1m3!1d4872.232948764011!2d4.889200000000001!3d52.368308!3m2!1i1024!2i768!4f13.1!3m3!1m2!1s0x47c609c193a4380f%3A0xccfdbd1232ff182d!2sAula%20UvA!5e0!3m2!1sen!2snl!4v1707607227284!5m2!1sen!2snl" width="600" height="450" style="border:0;" allowfullscreen="" loading="lazy" referrerpolicy="no-referrer-when-downgrade"></iframe>


+ **🕐Starting Time:**
  
  *Please arrive 30 minutes before starting time.*

+ **Program:**
  + 




`html_pretty` in the [**prettydoc**](https://github.com/yixuan/prettydoc/) package is a new output format for creating HTML documents from R Markdown files. `html_pretty` is more lightweight compared to `html_document`, and is more stylish than `html_vignette` when creating package vignettes.

## New Styles

`html_pretty` currently supports three page themes (`cayman`, `tactile` and `architect`), and two syntax highlight styles (`github` and `vignette`). The theme and highlight styles can be specified in the document metadata, for example:

``` yaml
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
```

## Your Familiar Tools

Feel free to use the `knitr` infrastructure with dozens of tunable options in your document.

```{r fig.width=6, fig.height=6, fig.align='center'}
set.seed(123)
n <- 1000
x1  <- matrix(rnorm(n), ncol = 2)
x2  <- matrix(rnorm(n, mean = 3, sd = 1.5), ncol = 2)
x   <- rbind(x1, x2)
head(x)
smoothScatter(x, xlab = "x1", ylab = "x2")
```

You can include code snippets of languages other than R, but note that the block header has no curly brackets around the language name.

``` cpp
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
    return x * 2;
}
```

You can also write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes[^1], and tables, e.g. using `knitr::kable()`.

[^1]: A footnote here.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(iris, 10))
```

## Stay Tuned

Please visit the [development page](https://github.com/yixuan/prettydoc/) of the `prettydoc` package for latest updates and news. Comments, bug reports and pull requests are always welcome.
