---
title: "Fabio Defense"
author: "Document Author"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
    toc: true
    toc_depth: 2
---

<h1> Welcome to Fabio's Defense Website </h1>

- Event info (time, location, duration, dress code, similar to emails from other defense)
- RSVPs link to google form where we collect emails (optional) and allow down of calendar invite - HERE add both dissertation, borrel, and party
- Calendar invite with both dissertation + borrel and party invites - kinda like phd club
- Link to maps dissertation + borrel and party location
- (Optional) Summary of dissertation, maybe abstract with the hopefully cute and badass cover
- Secret gift page with donation payment options - use IBAN, tikkie, my paypal or ask if sophia can set it up
- Insta page + Hashtag
- 

Here you will find all the information you for the big day! ✨

`html_pretty` in the [**prettydoc**](https://github.com/yixuan/prettydoc/) package is a new output format for creating HTML documents from R Markdown files. `html_pretty` is more lightweight compared to `html_document`, and is more stylish than `html_vignette` when creating package vignettes.

## New Styles

`html_pretty` currently supports three page themes (`cayman`, `tactile` and `architect`), and two syntax highlight styles (`github` and `vignette`). The theme and highlight styles can be specified in the document metadata, for example:

``` yaml
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
```

## Your Familiar Tools

Feel free to use the `knitr` infrastructure with dozens of tunable options in your document.

```{r fig.width=6, fig.height=6, fig.align='center'}
set.seed(123)
n <- 1000
x1  <- matrix(rnorm(n), ncol = 2)
x2  <- matrix(rnorm(n, mean = 3, sd = 1.5), ncol = 2)
x   <- rbind(x1, x2)
head(x)
smoothScatter(x, xlab = "x1", ylab = "x2")
```

You can include code snippets of languages other than R, but note that the block header has no curly brackets around the language name.

``` cpp
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
    return x * 2;
}
```

You can also write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes[^1], and tables, e.g. using `knitr::kable()`.

[^1]: A footnote here.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(iris, 10))
```

## Stay Tuned

Please visit the [development page](https://github.com/yixuan/prettydoc/) of the `prettydoc` package for latest updates and news. Comments, bug reports and pull requests are always welcome.
